Efficient forwards-time simulation with ancestral recombination graphs

### 2017-08-26 forwards_paper.tex
added mutations to WF writeup

\paragraph{Iterate:}
We then step through the generations:
\plr{Add mutations to this:}
\begin{lstlisting}[language=Python]
for t in 1:T:
    for i in 0:N-1:
        if random.uniform() > death_prob:
            new_pop[i] = pop[i]
        else:
            u = nodes.num_rows  # the ID of the new individual
            new_pop[i] = u
            nodes.add_row(time = T-t)
            a = random.sample(pop)
            b = random.sample(pop)
            bp = random.sample(0:L)
            if bp > 0:
                edgesets.add_row(left=0, right=bp,
                                  parent=a, children=(u,))
            if bp < L:
                edgesets.add_row(left=bp, right=L,
                                  parent=b, children=(u,))
    pop = new_pop
\end{lstlisting}

>>>>

\paragraph{Iterate:}
We then step through the generations,
using the functions \texttt{random\_mutation} and \texttt{random\_allele}
to choose positions and alleles for mutations, respectively:
\begin{lstlisting}[language=Python]
for t in 1:T:
    for i in 0:N-1:
        if random.uniform() > death_prob:
            new_pop[i] = pop[i]
        else:
            u = nodes.num_rows  # the ID of the new individual
            new_pop[i] = u
            nodes.add_row(time = T-t)
            a = random.sample(pop)
            b = random.sample(pop)
            bp = random.sample(0:L)
            if bp > 0:
                edgesets.add_row(left=0, right=bp,
                                  parent=a, children=(u,))
            if bp < L:
                edgesets.add_row(left=bp, right=L,
                                  parent=b, children=(u,))
            num_muts = random.poisson(mut_rate)
            for j in 1:num_muts:
                pos = random_mutation()
                if pos not in sites.position:
                    s = sites.num_rows
                    sites.add_row(position=pos, 
                           ancestral_state=random_allele())
                else:
                    s = sites.position.index(pos)
                mutations.add_row(site=s, node=u, 
                           derived_state=random_allele())
    pop = new_pop
\end{lstlisting}
